---
title: "project"
output: html_document
---

1. Downloading data

```{r include=FALSE}
library (rjson)
library(jsonlite)
library(tibble)
library(readr)
library(readxl)

yelp <- fromJSON("~/3rd course/2 term/project/Saint-Petersburg_1.json")
str(yelp)
yelp_flat <- flatten(yelp)
yelp_tbl <- as_data_frame(yelp_flat)
df <- yelp_flat[!is.na(yelp_flat$tripAdvisor_link),]


drops <- c("foursquare_checkinsCount","foursquare_ratingVotes", "foursquare_userCount","open_hours.7","instagram_visitorsNumber", "tripAdvisor_link", "foursquare_rating")
df= df[ , !(names(df) %in% drops)]
df = distinct(df, title, .keep_all = TRUE)

subway <- read_excel("~/3rd course/2 term/project/Subway.xlsx")

```

2. Working hours

```{r include=FALSE}

library(tidyr)
df$open_hours.0[df$open_hours.0 == 'NULL'] <- list(c(0,0))
df$open_hours.1[df$open_hours.1 == 'NULL'] <- list(c(0,0))
df$open_hours.2[df$open_hours.2 == 'NULL'] <- list(c(0,0))
df$open_hours.3[df$open_hours.3 == 'NULL'] <- list(c(0,0))
df$open_hours.4[df$open_hours.4 == 'NULL'] <- list(c(0,0))
df$open_hours.5[df$open_hours.5 == 'NULL'] <- list(c(0,0))
df$open_hours.6[df$open_hours.6 == 'NULL'] <- list(c(0,0))
unnest_time= function(var, name1, name2) { df= df%>%
  dplyr::mutate(var = purrr::map(var, setNames, c("name1","name2"))) %>%
  unnest_wider(var)
}
df = df%>%
  dplyr::mutate(open_hours.0 = purrr::map(open_hours.0, setNames, c("open0","close0"))) %>%
  unnest_wider(open_hours.0)

df = df%>%
  dplyr::mutate(open_hours.1 = purrr::map(open_hours.1, setNames, c("open1","close1"))) %>%
  unnest_wider(open_hours.1)

df = df%>%
  dplyr::mutate(open_hours.2 = purrr::map(open_hours.2, setNames, c("open2","close2"))) %>%
  unnest_wider(open_hours.2)

df = df%>%
  dplyr::mutate(open_hours.3 = purrr::map(open_hours.3, setNames, c("open3","close3"))) %>%
  unnest_wider(open_hours.3)

df = df%>%
  dplyr::mutate(open_hours.4 = purrr::map(open_hours.4, setNames, c("open4","close4"))) %>%
  unnest_wider(open_hours.4)

df = df%>%
  dplyr::mutate(open_hours.5 = purrr::map(open_hours.5, setNames, c("open5","close5"))) %>%
  unnest_wider(open_hours.5) 

df = df%>%
  dplyr::mutate(open_hours.6 = purrr::map(open_hours.6, setNames, c("open6","close6"))) %>%
  unnest_wider(open_hours.6)

df$open0= as.integer(df$open0/100)
df$open1= as.integer(df$open1/100)
df$open2= as.integer(df$open2/100)
df$open3= as.integer(df$open3/100)
df$open4= as.integer(df$open4/100)
df$open5= as.integer(df$open5/100)
df$open6= as.integer(df$open6/100)
df$close0=as.integer(df$close0/100)
df$close1=as.integer(df$close1/100)
df$close2=as.integer(df$close2/100)
df$close3=as.integer(df$close3/100)
df$close4=as.integer(df$close4/100)
df$close5=as.integer(df$close5/100)
df$close6=as.integer(df$close6/100)
```


3. Feature Ingineering. 

```{r include=FALSE}
#Feature Ingineering 
df2 = df[df$close0 == "24",]
df$noctidial = ifelse(df$title %in% df2$title, "TRUE", "FALSE")
df$id= rownames(df)
```

```{r include=FALSE}
df$category[df$category == 'c("Museums & Libraries", "Nature & Parks")'] <- "Museums & Libraries"
df$category[df$category == 'c("Sights & Landmarks", "Nature & Parks")'] <- "Sights & Landmarks"
df$category[df$category == 'c("Sights & Landmarks", "Museums & Libraries")'] <- "Museums & Libraries"
df$category[df$category == 'c("Museums & Libraries", "Concerts & Shows")'] <- "Museums & Libraries"
df$category[df$category == 'c("Sights & Landmarks", "Concerts & Shows")'] <- "Concerts & Shows"
df$category[df$category == 'c("Sights & Landmarks", "Museums & Libraries", "Nature & Parks")'] <- "Museums & Libraries"
unique(df$category)

df$free[df$category=='Sights & Landmarks']<-1
df$free[df$category=='Museums & Libraries']<-0
df$free[df$category=='Nature & Parks']<-1
df$free[df$category=='Concerts & Shows']<-0
table(df$free)
```

4. Creating must visit places

```{r include=FALSE}
library (dplyr)

df= dplyr:: mutate(df, must_visit= df$tripAdvisor_reviewsNumber)

df= df %>% select (-tripAdvisor_reviewsNumber)

summary(df$must_visit)

approval_condition = (df$must_visit >=500)

df$must_visit = ifelse(approval_condition, "1", "0")

df$must_visit <- as.numeric(df$must_visit)

```


5.Clustering 

```{r}
library(cluster.datasets)
places = df %>% select (free, duration, title)
places$id= rownames(places)
places$duration = as.numeric(places$duration)

places$duration_15 = ifelse(places$duration == 15, "1", "0") %>% as.numeric()
places$duration_60 = ifelse(places$duration == 60, "1", "0") %>% as.numeric()
places$duration_120 = ifelse(places$duration == 120, "1", "0") %>% as.numeric()
places = places %>% select(-duration)

id = places %>% select(id, title)
id$id = as.numeric(id$id)
places = places %>% select(-title)
places$id = as.numeric(places$id)
scaled_places = as.matrix(scale(places))

place.average = hclust(dist(scaled_places), method="average")
#plot(place.average, main="Average Linkage", xlab="", sub="", cex=.9)
hclusters = cutree(place.average, k = 4)

id = inner_join(id, places)
title = id %>% na.omit()
df$id = as.numeric(df$id)
df_cluster = left_join(title, df)

df_cluster$hclust = hclusters
cluster1 = df_cluster %>% filter(hclust==1)
cluster2 = df_cluster %>% filter(hclust==2)
cluster3 = df_cluster %>% filter(hclust==3)
cluster4 = df_cluster %>% filter(hclust==4)
df=df_cluster

```


6. Recommendation system
```{r}
#Filters to choose cluster number
free='yes'
duration=15

if (free=='yes' & duration==15) {
  df_shiny= cluster1
}

if (free=='no' & duration==15) {
  df_shiny= rbind(cluster1, cluster3)
}

if (duration==120 & free=='no') {
  df_shiny= df
}

if (duration==120 & free=='yes') {
  df_shiny= rbind(cluster1, cluster4)
}

if (free=='no' & duration==60) {
  do.call("rbind", list(cluster1, cluster3, cluster4))
}

if (free=='yes' & duration==60) {
  df_shiny= rbind(cluster1, cluster4)
}


#Category
category="Sights & Landmarks"
if (category=="Sights & Landmarks") {
    df_shiny= df_shiny[df_shiny$category=="Sights & Landmarks",]
    }
if (category=="Museums & Libraries") {
    df_shiny= df_shiny[df_shiny$category=="Museums & Libraries",]
    }
if (category=="Concerts & Shows") {
    df_shiny= df_shiny[df_shiny$category=="Concerts & Shows",]
    }
if (category=="Nature & Parks") {
    df_shiny= df_shiny[df_shiny$category=="Nature & Parks",]
    }


#Type
top_place="yes"
if (top_place=="yes") {
    df_shiny= df_shiny[df_shiny$must_visit==1,]} 
if (top_place=="no") {
  df_shiny= df_shiny[df_shiny$must_visit==0,]}

#Wday and time
wday= "Monday"
time=24 

if (wday=="Monday")  {
    df_shiny= df_shiny[time>=df_shiny$open0,]
    df_shiny= df_shiny[time<=df_shiny$close0,]
} 
if (wday=="Tuesday") {
    df_shiny= df_shiny[time>=df_shiny$open1,]
    df_shiny= df_shiny[time<=df_shiny$close1,]
} 
if (wday=="Wednesday") {
    df_shiny= df_shiny[time>=df_shiny$open2,]
    df_shiny= df_shiny[time<=df_shiny$close2,]
} 
if (wday=="Thursday") {
    df_shiny= df_shiny[time>=df_shiny$open3,]
    df_shiny= df_shiny[time<=df_shiny$close3,]
} 
if (wday=="Friday") {
    df_shiny= df_shiny[time>=df_shiny$open4,]
    df_shiny= df_shiny[time<=df_shiny$close4,]
} 
if (wday=="Saturday ") {
    df_shiny= df_shiny[time>=df_shiny$open5,]
    df_shiny= df_shiny[time<=df_shiny$close5,]
} 
if (wday=="Sunday ") {
    df_shiny= df_shiny[time>=df_shiny$open6,]
    df_shiny= df_shiny[time<=df_shiny$close6,]}
    

#Subway
close="yes"
subway="Parnas"


```


8. Randon place generator

```{r}
random= sample_n(df,1)
random
cat("Place name: ", random$title, "Adress: ", random$address, "Category: ", random$category , sep= '\n')

```
9. Distance between landmarks and subway stations

#сделат ьслайдер для кол-ва достопримечательностей

```{r}
#Special icon for metro 
icon_metro<- makeAwesomeIcon(icon= 'home', markerColor = 'orange', iconColor = 'black')
```


```{r}
library(geosphere)
library(readxl)
library(leaflet)
Subway$x1 = as.numeric(Subway$x1)
Subway$y1 = as.numeric(Subway$y1)
xy = cbind(c(df$lat), c(df$lng))
m = cbind(c(Subway$x1),c(Subway$y1))
distm(x = xy, y = m)
m1 = as.data.frame(m)
xy1 = as.data.frame(xy)
dis = distm(x = xy, y = m)
dis2 = as.data.frame(dis)
colnames(dis2) = Subway$`Subway station`


#Filter
dis3 = as.matrix(dis2)
dis3[dis3 >=2000] <- NA
dis4 = as.data.frame(dis3)
dis4$cites = df$title
dis4 = arrange_all(dis4)
a='Spasskaya'

#Function
citesearch <- function(a) {
dis5 = select(dis4, c(a, "cites"))
dis5 = na.omit(dis5)
b = length(dis5$cites)
if (b == 0) {
print("Достопримечательностей нет, соррямба")
} else {if (b<=10) {
dis5$cites
} else {
dis5 = dis5[1:10,]
dis5$cites
}
}
write.csv(dis5, file = "funcites")
dis5$cites
colnames(Subway) = c("station", "lat", "lng", "Location")
subcord = filter(Subway, station == a)
subcord = select(subcord, 1:3)
colnames(subcord) = c("title", "lat", "lng")
funcites = read.csv("~/funcites")
funcites = funcites$cites
df$cord = df$title %in% funcites
df = filter(df, cord == TRUE)
df = select(df, title, lat, lng)
full = rbind(subcord, df)
leaflet(full) %>% addTiles() %>%
addMarkers(~lng[-1], ~lat[-1], popup = ~title[-1]) %>%
addAwesomeMarkers(~lng[1], ~lat[1], label = ~title[1],icon = icon_metro,
labelOptions = labelOptions(noHide = T, direction = "bottom",
style = list(
"color" = "black",
"font-family" = "serif",
"font-style" = "bold",
"box-shadow" = "3px 3px rgba(0,0,0,0.25)",
"font-size" = "12px",
"border-color" = "rgba(0,0,0,0.5)"))) %>%
addMeasure()
}
citesearch(a)


10. Shiny App
library(shiny)
library(shinyWidgets)
library(rjson)
library(jsonlite)
library(tibble)
library(dplyr)
library(tidyr)
library(cluster.datasets)
library(readr)
library(readxl)
library(geosphere)
library(leaflet)
library(htmltools)

#Downloading data
load("~/shared/minor3_2019_13/DEPLOY/for_app")
load("~/shared/minor3_2019_13/DEPLOY/clusters")
#Downloading subway data
Subway = read_excel("~/shared/minor3_2019_13/DEPLOY/Subway.xlsx")
dis4 = read.csv("~/shared/minor3_2019_13/DEPLOY/distances.csv")
icon_metro<- makeAwesomeIcon(icon= 'home', markerColor = 'orange', iconColor = 'black')



ui <- fluidPage(
  tags$head(tags$style(
    HTML('
         #sidebar {
            background-color: "#e60000";
        }

        body, label, input, button, select { 
          font-family: "Garamond";
        }')
  )),
  
  #background
  setBackgroundColor(
    color = c("#ffffff", "#fff7e6"),
    gradient = "radial",
    direction = c("top", "left")
  ),
  
  # Application title
  titlePanel(
    h1("Welcome to Saint-Petersburg", align = "center")
  ),
  
  fluidRow(
    column(3,
           helpText("Use this column, if you would like to choose filters. And make sure, that 'Get randomly!' is unticked!")
    ),
    
    column(3,
          helpText("Use this column, if you would like to get random recommendation")
    )
    
  ),
  
  fluidRow(
        column(3,
           radioButtons("MustVisit", "Have you ever been to St. Petersburg?",
                        choices = list("Yes" = 1, "No" = 2),
                        selected = 2)
           ),
    
    column(3,
           checkboxInput("randomly", "Get randomly!", value = FALSE),
            )
    
  ),
  
  
  fluidRow(
    column(3,
           sliderInput("time", "When would you like to visit?",
                       min = 1, max = 24, value = c(10, 18))    
    ),
    
    column(3,
            sliderInput("number", "How many places would you like to get?",
                       min = 1, max = 10, value = 5)      
    )
    
  ),
  
  
  fluidRow(
    column(3,
           selectInput("subway",
                       "Choose metro stations which are closest to you",
                       choices = Subway[2],
                       selected = c(""),
                       multiple = FALSE)      
    ),
    
    column(3,
           numericInput("cluster", "Try your luck and type a digit from 1 to 5!",
                        value = 3, min = 1, max = 5, step = 1,
                        width = NULL)      
    )
  ),
  
  
  fluidRow(
    column(3,
           selectInput("category",
                       "Choose category of a place",
                       choices = c("Sights & Landmarks", "Museums & Libraries",
                                   "Concerts & Shows", "Nature & Parks"),
                       multiple = FALSE)   
    ),
    
    column(3,
           submitButton("Ready!")      
    )
    
  ),

  
  fluidRow(
    column(3,
           radioButtons("wday", "Choose day",
                        choices = list("Monday" = 1, "Tuesday" = 2,
                                       "Wednesday" = 3, "Thursday" = 4,
                                       "Friday" = 5, "Saturday" = 6,
                                       "Sunday" = 7))     
    ),
    
    column(3,
           
    )
    
  ),
  
  
  fluidRow(
    column(3,
           sliderInput("duration", "How much time (min) would you like to spend at the place?",
                       min = 0, max = 120, step = 15, value = c(15, 60))
    ),
    
    column(3,
           
    )
    
  ),
  
  
  fluidRow(
    column(3,
           checkboxInput("free",
          "I want something available for free",
          value = FALSE)     
    ),
    
    column(3,
           
    )
    
  ),
  
  
  fluidRow(
    column(3,
           submitButton("Ready!")     
    ),
    
    column(3,
           
    )
    
  ),
      

      
    
    # Show a table and a map
    mainPanel(
      img(src = "https://i.ibb.co/HhT4fLX/dvor.jpg", height = 300, width = 500),
      h3("the city for everyone"),
      tabsetPanel(#color = "pink",
        tabPanel("Map", leafletOutput("map")),
        tabPanel("Table", tableOutput("table"))
      ))
  )






server <- function(input, output, session) { 
  
  output$table <- renderTable ({ 

    if (input$randomly == T) 
    {if (input$cluster == 1) {
      df_cluster = filter(df_cluster, cluster == 1)
      random = sample_n(df_cluster, input$number)
      select(random, title, address)
      } else if (input$cluster == 2) {
        df_cluster = filter(df_cluster, cluster == 2)
        random = sample_n(df_cluster, input$number)
        select(random, title, address)
      } else if (input$cluster == 3) {
        df_cluster = filter(df_cluster, cluster == 3)
        random = sample_n(df_cluster, input$number)
        select(random, title, address)
      } else if (input$cluster == 4) {
        df_cluster = filter(df_cluster, cluster == 4)
        random = sample_n(df_cluster, input$number)
        select(random, title, address, cluster)
      } else if (input$cluster == 5) {
        df_cluster = filter(df_cluster, cluster == 5)
        random = sample_n(df_cluster, input$number)
        select(random, title, address)
      } else { 
       random = sample_n(df, input$cluster)
      select(random, title, address)}}
    else {
    LOL =  if (input$MustVisit == 2) {
      df = filter(df, must_visit == 1) #%>% sample_n(input$number)
      if (input$wday==1)
        df = filter(df, open0 <= input$time[1] & close0 >= input$time[2])
      else if (input$wday==2)
        df = filter(df, open1 <= input$time[1] & close1 >= input$time[2])
      else if (input$wday==3)
        df = filter(df, open2 <= input$time[1] & close2 >= input$time[2])
      else if (input$wday==4)
        df = filter(df, open3 <= input$time[1] & close3 >= input$time[2])
      else if (input$wday==5)
        df = filter(df, open4 <= input$time[1] & close4 >= input$time[2])
      else if (input$wday==6)
        df = filter(df, open5 <= input$time[1] & close5 >= input$time[2])
      else (input$wday == 7)
      df = filter(df, open6 <= input$time[1] & close6 >= input$time[2])}
      else  if (input$MustVisit == 1)
        df = filter(df, must_visit == 0) #%>% sample_n(input$number)
      if (input$wday==1)
        df = filter(df, open0 <= input$time[1] & close0 >= input$time[2])
      else if (input$wday==2)
        df = filter(df, open1 <= input$time[1] & close1 >= input$time[2])
      else if (input$wday==3)
        df = filter(df, open2 <= input$time[1] & close2 >= input$time[2])
      else if (input$wday==4)
        df = filter(df, open3 <= input$time[1] & close3 >= input$time[2])
      else if (input$wday==5)
        df = filter(df, open4 <= input$time[1] & close4 >= input$time[2])
      else if (input$wday==6)
        df = filter(df, open5 <= input$time[1] & close5 >= input$time[2])
      else (input$wday == 7)
      df = filter(df, open6 <= input$time[1] & close6 >= input$time[2])
    
    LOL2 = if (input$category=="Sights & Landmarks")
      LOL = filter(LOL, category == "Sights & Landmarks")
    else if (input$category=="Museums & Libraries") 
      LOL = filter(LOL, category == "Museums & Libraries")
    else if (input$category=="Concerts & Shows")
      LOL = filter(LOL, category == "Concerts & Shows")
    else  LOL = filter(LOL, category == "Nature & Parks")
    
    LOL3 = if (input$free == TRUE) 
      LOL2 = filter(LOL2, free ==1)
    else LOL2
    
    difference = input$duration[2] - input$duration[1]
    difference = difference/15
    final = if (difference == 1) 
      LOL3 = filter(LOL3, duration_15 == 1 | duration_60 == 1 | duration_120 == 1) #%>% select(title, address)
    else if (difference > 1 & difference <=4)
      LOL3 = filter(LOL3, duration_60 == 1 | duration_120 == 1) #%>% select(title, address)
    else LOL3 = filter(LOL3, duration_120 == 1)
    select(final, title, address)}
  })
  
  
  output$map <- renderLeaflet({
    
    if (input$randomly == T) 
    {random = sample_n(df, input$number)
    random = select(random, title, lng, lat)
    station2 = as.character(input$subway)
    Subway = select(Subway, 2:5)
    colnames(Subway) = c("station", "lat", "lng", "Location")
    subcord1 = filter(Subway, station2 == station)
    subcord1 = select(subcord1, 1:3)
    colnames(subcord1) = c("title", "lat", "lng")
    full2 = rbind(subcord1, random)
    full2$lat = as.numeric(full2$lat)
    full2$lng = as.numeric(full2$lng)
    leaflet(full2) %>% addTiles() %>%
      addMarkers(~lng[-1], ~lat[-1], popup = ~title[-1]) %>%
      addMarkers(~lng[1], ~lat[1], label = ~title[1],
                 labelOptions = labelOptions(noHide = T, direction = "bottom",
                                             style = list(
                                               "color" = "black",
                                               "font-family" = "Garamond",
                                               "font-style" = "bold",
                                               "box-shadow" = "3px 3px rgba(0,0,0,0.25)",
                                               "font-size" = "12px",
                                               "border-color" = "rgba(0,0,0,0.5)"))) %>% 
      addMeasure()
    }
    else {{
      LOL =  if (input$MustVisit == 2) {
      df = filter(df, must_visit == 1) #%>% sample_n(input$number)
      if (input$wday==1)
        df = filter(df, open0 <= input$time[1] & close0 >= input$time[2])
      else if (input$wday==2)
        df = filter(df, open1 <= input$time[1] & close1 >= input$time[2])
      else if (input$wday==3)
        df = filter(df, open2 <= input$time[1] & close2 >= input$time[2])
      else if (input$wday==4)
        df = filter(df, open3 <= input$time[1] & close3 >= input$time[2])
      else if (input$wday==5)
        df = filter(df, open4 <= input$time[1] & close4 >= input$time[2])
      else if (input$wday==6)
        df = filter(df, open5 <= input$time[1] & close5 >= input$time[2])
      else (input$wday == 7)
      df = filter(df, open6 <= input$time[1] & close6 >= input$time[2])}
      else  if (input$MustVisit == 1)
        df = filter(df, must_visit == 0) #%>% sample_n(input$number)
      if (input$wday==1)
        df = filter(df, open0 <= input$time[1] & close0 >= input$time[2])
      else if (input$wday==2)
        df = filter(df, open1 <= input$time[1] & close1 >= input$time[2])
      else if (input$wday==3)
        df = filter(df, open2 <= input$time[1] & close2 >= input$time[2])
      else if (input$wday==4)
        df = filter(df, open3 <= input$time[1] & close3 >= input$time[2])
      else if (input$wday==5)
        df = filter(df, open4 <= input$time[1] & close4 >= input$time[2])
      else if (input$wday==6)
        df = filter(df, open5 <= input$time[1] & close5 >= input$time[2])
      else (input$wday == 7)
      df = filter(df, open6 <= input$time[1] & close6 >= input$time[2])}
    
    LOL2 = if (input$category=="Sights & Landmarks")
      LOL = filter(LOL, category == "Sights & Landmarks")
    else if (input$category=="Museums & Libraries") 
      LOL = filter(LOL, category == "Museums & Libraries")
    else if (input$category=="Concerts & Shows")
      LOL = filter(LOL, category == "Concerts & Shows")
    else  LOL = filter(LOL, category == "Nature & Parks")
    
    LOL3 = if (input$free == TRUE) 
      LOL2 = filter(LOL2, free ==1)
    else LOL2
    
    difference = input$duration[2] - input$duration[1]
    difference = difference/15
    final = if (difference == 1) 
      LOL3 = filter(LOL3, duration_15 == 1 | duration_60 == 1 | duration_120 == 1)
    else if (difference > 1 & difference <=4)
      LOL3 = filter(LOL3, duration_60 == 1 | duration_120 == 1)
    else LOL3 = filter(LOL3, duration_120 == 1)
    station1 = as.character(input$subway)
    colnames(dis4) = c("X", Subway$`Subway station`, "cites")
    dis5 = select(dis4, c(station1, "cites"))
    dis5 = na.omit(dis5)
    dis5 = dis5$cites
    Subway = select(Subway, 2:5)
    colnames(Subway) = c("station", "lat", "lng", "Location")
    subcord = filter(Subway, station1 == station)
    subcord = select(subcord, 1:3)
    colnames(subcord) = c("title", "lat", "lng")
    final$cord = final$title %in% dis5
    final = filter(final, cord == TRUE)
    final = select(final, c("title", "lat", "lng"))
    full = rbind(subcord, final)
    full$lat = as.numeric(full$lat)
    full$lng = as.numeric(full$lng)
    leaflet(full) %>% addTiles() %>%
      addMarkers(~lng[-1], ~lat[-1], popup = ~title[-1]) %>%
      addAwesomeMarkers(~lng[1], ~lat[1], label = ~title[1], icon = icon_metro,
                 labelOptions = labelOptions(noHide = T, direction = "bottom",
                                             style = list(
                                               "color" = "black",
                                               "font-family" = "Garamond",
                                               "font-style" = "bold",
                                               "box-shadow" = "3px 3px rgba(0,0,0,0.25)",
                                               "font-size" = "12px",
                                               "border-color" = "rgba(0,0,0,0.5)"))) %>% 
      addMeasure()}
  })

}

shinyApp(ui = ui, server = server)

